
# ORD Project Plan

## WP0: Coordination and Planning

```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(readr)
library(dplyr)
tbl <- read_csv("data/tables/tbl-02-wp-activities-research-questions.csv")

a <- tbl |>
    filter(WP == "WP0") |>
    pull(`Project Activity`)

r <- tbl |>
    filter(WP == "WP0") |>
    pull(`Research Question`)



```


::: {.callout-note}

# Activities and Research Questions

`r a[1]`

`r a[2]`

`r r[1]`

`r r[2]`

:::


### Goals {.unnumbered}

During the starting stage of our project, we coordinate with major public data providers and involve data sources in our planning early on. We do so in order to establish and maintain active, lively communication between public data providers and the scientific usage community. 

<!-- activities & RQs -->
Publicly available economic data provided by the Federal Statistical Office (FSO), the Secretariat of Economic affairs (SECO), the Swiss National Bank (SNB) as well as regional Statistical Offices are important sources for economic research and monitoring of the Swiss economy. To develop an ORD spirit and a community of a data providers and scientific users of the data, it is crucial to involve these public institutions early on. Early dialogue helps to avoid reduncancies with existing data community initiatives and to develop a common understanding of *open data*, machine readability and datasets of priority. 

One of the core parts of our approach is to leverage the investment into open data and strengthen connection between academia and federal and regional administration is to integrate public data into academic teaching. To explore how to effectively use the joint expertise of public data providers, domain experts, data stewards of the ETH domain and data engineers, we launch a series of monthly meetups early in the process. The meetups are designed to foster inclusive expert discussions through publicly pre-circulated content. We are working to integrate our meetup series into the academic curriculum at ETH, but keep the series open to interested participants beyond academia. 



## WP1: Homogenization of Data Processing Across Data Sources


```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(readr)
library(dplyr)
tbl <- read_csv("data/tables/tbl-02-wp-activities-research-questions.csv")

a <- tbl |>
    filter(WP == "WP1") |>
    pull(`Project Activity`)

r <- tbl |>
    filter(WP == "WP1") |>
    pull(`Research Question`)



```


::: {.callout-note}

# Activities and Research Questions

`r a[1]`

`r a[2]`

`r a[3]`

`r r[1]`

`r r[2]`

`r r[3]`

:::


### Goals {.unnumbered}

<!-- communication through the opents project, code as communication channel --> 

In work package 1 (WP1), we lay the technical foundation to re-publish public data as a machine readable resource. Our approaches use license cost free open source software and aims to publish not only the data but also the technical framework in order to ensure reproducibility and comply with FAIR principles. In addition, the *opents* project embraces an infrastructure-as-code approach and publishes this information on the runtime environment in order to facilitate operation of an instance of the *opents* framework through others. 

Because an active community is inevitable to keep sustainable, i.e., maintained, we chose the R Project for Statistical Computing as our main programming language for the implementation of the framework. R is known for its large and inclusive community with its annual user conferences and vibrant local communities (insert figure Ben's community explorer, article on useR!, hosted in 2021). 

In a first implementation step, based on our long term experience as consumers of public data, we disentangle common parts of the data ingestion process from dataset or provider specific idiosyncrasies. When monitoring the Swiss economy, we compare publication dates, download files or consume APIs. 

<!--- Insert schematic process -->

In the process, operations such as downloads, exchange with industry standard APIs and comparison of publication are relatively common across datasets and providers while data transformation can be very specific. We compose these common parts in a opents-core R package. 


next up: modular packages. 



 through tasks as monitors of the Swiss economy (KOF), we identify common ground 

accountability, monitoring




ORD excellence

- critical problem
- beyond state of the art
- integration of existing ORD practices (open source, reproducibility)

RQ1 components of a framework

- data repository
- common source code (reuse)
- source specific source code (modular) (RQ2)
- standards for data and data description -> FAIR
- community 
- runtime environment


RQ3
- open source, free of license costs
- interactivity
- language / wording
- application examples / interactivity
- community support -> matrix 
- portfolio type of examples (confidence in approach)




- implement data provider specific code for core datasets (specific)
- develop documentation that fosters inclusion of the community, encourages use of the library AND resulting datasets
- prepare for publication of engine
- reproducible research



## WP2: Publication

```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(readr)
library(dplyr)
tbl <- read_csv("data/tables/tbl-02-wp-activities-research-questions.csv")

a <- tbl |>
    filter(WP == "WP2") |>
    pull(`Project Activity`)

r <- tbl |>
    filter(WP == "WP2") |>
    pull(`Research Question`)



```



::: {.callout-note}

# Activities and Research Questions

`r a[1]`

`r a[2]`

`r a[3]`

`r a[4]`

`r r[1]`

`r r[2]`

`r r[3]`

`r r[4]`

:::


### Goals



## WP3: Community Activation

```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(readr)
library(dplyr)
tbl <- read_csv("data/tables/tbl-02-wp-activities-research-questions.csv")

a <- tbl |>
    filter(WP == "WP3") |>
    pull(`Project Activity`)

r <- tbl |>
    filter(WP == "WP3") |>
    pull(`Research Question`)



```


::: {.callout-note}

# Activities and Research Questions

`r a[1]`

`r a[2]`


`r r[1]`

`r r[2]`



:::


### Goals